\documentclass[10pt, a4paper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue
}
\usepackage{mdwlist}
\begin{document}
\thispagestyle{empty}
\begin{flushright}
\small \today
\end{flushright}
\begin{center}
\textbf{\Large Matthew G. Belisle}
\rule{\linewidth}{0.5mm}
\end{center}
\begin{flushright}
\begin{minipage}[h]{0.25\linewidth}\small
\begin{flushleft}
406-599-4238\\
\href{mailto:mgbelisle@gmail.com}{mgbelisle@gmail.com}\\
85 Pioneer Rd\\
Three Forks, MT 59752
\end{flushleft}
\end{minipage}
\end{flushright}
\textbf{Job Interests}
\begin{itemize*}
  \item Pentesting
  \item Software engineering
  \item Japanese to English translation
\end{itemize*}
\textbf{Experience}
\begin{itemize*}
  \item \emph{Software Engineer} (Mar. 2012 to present)\\
    Workiva, IR Team (Bozeman, MT, \url{https://www.wdesk.com})
    \begin{itemize*}
      %% For InfoSec
    \item Wrote many services, including fastpath (Java), gremlin (Go), parts of graph and admin clients (Dart)
    \item Implemented auth for the Messaging team in messaging-sdk Java
    \item Wrote the go-auth v2 token library from scratch using only Go's stdlibs
    \item Consumed Workiva auth for many services including graph server/client, fastpath, graph admin, viewer
    \item Consumed Microsoft, Twitter, Github, Facebook, AWS, Google auth on side projects
    \item Wrote the iam-cli util from scratch using only Go's stdlibs (2/3 legged tokens, bigsky sessions)
    \item Wrote a couple major features for Smithy and Zuul
    \item Consumed smithy/shipyard/skynet on many projects including fastpath, graph, graph admin
    \item Wrote an asynchronous API over messaging-sdk that did instance routing and large payloads efficiently
    \item Wrote many of the iam-services endpoints in Python
    \item Helped many teams troubleshoot CORS, CSP, SSL certs, websockets
    \item Found and reported twelve high severity vulnerabilities in the Workiva platform in the last year
      %% https://jira.atl.workiva.net/browse/CERT-1702
      %% https://jira.atl.workiva.net/browse/SEC-13740
      %% https://jira.atl.workiva.net/browse/SEC-13802
      %% https://jira.atl.workiva.net/browse/RED-1808
      %% https://jira.atl.workiva.net/browse/SEC-13932
      %% https://jira.atl.workiva.net/browse/SEC-13937
      %% https://jira.atl.workiva.net/browse/SEC-14019
      %% https://jira.atl.workiva.net/browse/SEC-14124
      %% https://jira.atl.workiva.net/browse/SEC-14143
      %% https://jira.atl.workiva.net/browse/SEC-14222
      %% https://jira.atl.workiva.net/browse/SEC-15242
      %% https://jira.atl.workiva.net/browse/FILE-1060
      
      %% \item Wrote a Python module to render our app's XML based charts as PDFs, SVGs, and PNGs
      %% \item Wrote AngularJS components for an HTML5 canvas based document viewer
      %% \item Wrote a Go package to deliver typesetting data over a REST interface
      %% \item Migrated many services in Dart, Go, and Java from REST and Websockets to Thrift
      %% \item Implemented OAuth2 exchanges for many apps, both browser side and server side
      %% \item Wrote a Workiva specific JWT/OAuth2 lib from Go's stdlibs
    \end{itemize*}
  \item \emph{Technical Support Engineer} (Mar. 2010 to Feb. 2012)\\
    RightNow Technologies, Customer Care Department\\
    (Bozeman, MT, \url{https://www.rightnow.com})
    \begin{itemize*}
      \item Provided technical support for RNT's proprietary web framework (both PHP and JS side)
      \item Provided general technical support for Japanese clients in Japanese
    \end{itemize*}
  \item \emph{Web Programmer} (Dec. 2008 to Feb. 2010)\\
    Elance (\url{https://www.elance.com})
    %% \begin{itemize*}
    %%   \item Wrote a django app for an Australian real-estate company MAE Pacific
    %%   \item Wrote a django app and doubled as system admin for a Chinese travel agency Shanghai Joy
    %% \end{itemize*}
  \item \emph{Japanese to English translator and technical editor} (Jun. 2006 to Feb. 2010)\\
    Excellence-English Editing (\url{https://www.excellence-english.com})
    % \begin{itemize*}
    %   \item Provided technical grammar editing of science journal articles written in English by Japanese scientists and doctors
    %   \item Translated approximately 70 powerpoint slides created by Sanyo Electric Co. that related to dry cell and Li-Ion batteries
    %   \item Translated a 5 part series on traditional Japanese fortune telling
    % \end{itemize*}
\end{itemize*}
\textbf{Education}
\begin{itemize*}
  \item \emph{Undergraduate} (Sep. 2006 through May 2009, not yet graduated)\\
    Montana State University Department of Computer Science\\
    (Bozeman, MT, \url{https://www.montana.edu})
    \begin{itemize*}
      \item Cumulative GPA of 3.64
    \end{itemize*}
  \item \emph{Foreign Exchange} (Sep. 2007 through Aug. 2008)\\
    Kumamoto University Department of Mechanical Engineering\\
    (Kumamoto Prefecture, Japan, \url{http://www.kumamoto-u.ac.jp})
  \item \emph{High School} (Sep. 2002 through Jun. 2006)\\
    The Oaks Classical Christian Academy\\
    (Spokane, WA, \url{https://www.theoakscca.org})
    \begin{itemize*}
      \item Graduated with a cumulative GPA of 3.94
    \end{itemize*}
\end{itemize*}
\textbf{Skills}
\begin{itemize*}
  \item Expertise with Java, Python, Go, App Engine, Datastore, MySQL, Thrift, AngularJS, HTML5, and Android SDK
  \item Familiarity with Git, Node, Docker, Grunt, Bower, Gulp, Browserify, some other dev tools
  \item Familiarity with Google Appengine, AWS, Digital Ocean platforms
  \item Familiarity with Linux things like Apache, Lighttpd, Systemd, Avahi, BATMAN, package creation
  \item Enjoys bacon and crypto libraries on a weekly basis
  \item Experience locating/exploiting vulnerabilities like XSS, CSRF, SQLI, XXE, birthday, timing attacks, DOS
\end{itemize*}
\textbf{Code Sample}
\begin{itemize}
  \item[] \url{https://github.com/mgbelisle/science/blob/master/paxos-demo/main.go}
\end{itemize}
\end{document}
